Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-05 paper/paper.tex
Update paper

During evaluation, Litrepl spawns a response reader process with a soft lock,
active until the interpreter completes and responds to an echo probe. If the
response exceeds the configured duration, Litrepl outputs a partial result tag,
which is recognized and reevaluated in subsequent runs.  Figure
\ref{fig:partial-result} shows an example partial result section.

As already mentioned, most of the resources are exposed to user via the
filesystem. The only added hidden state in the entire system resides in the
reader process, in a small finite state machine that handles special ASCII
characters used by some applications for text animation.

>>>>

During evaluation, Litrepl spawns a response reader process with a soft lock,
active until the interpreter completes and responds to an echo probe. The state
machine that operates the probe is the only added hidden state in the entire
system.

If the response exceeds the configured duration, Litrepl outputs a partial
result tag, which is recognized and reevaluated in subsequent runs.  Figure
\ref{fig:partial-result} shows an example partial result section.
